ms_figures

### 2023-03-31 ms_figures.Rmd
update file paths

```{r load_data}
# Set directories
datadir <- "outputs_20230330"
outdir <- "outputs_20230330"
```

@@

dom_source_ts_p <- dom_source_ts %>%
  filter(dom_source != "error export") %>%
  ggplot(aes(x = year, y = live_weight_t / 1000000, color = dom_source)) +
  geom_line() +
  scale_color_manual(values = c("#D38F35", "#114F59")) +
  theme_bw() +
  labs(x = "", y = "Live weight\nmillion tonnes", color = "Source") +
  theme(
    legend.position = "bottom",
    legend.box.margin=margin(t = -25)
  )

@@

>>>>

```{r load_data}
# Set directories
datadir <- "outputs"
outdir <- "outputs"
```

@@

dom_source_ts_p <- dom_source_ts %>%
  filter(dom_source != "error export") %>%
  ggplot(aes(x = year, y = live_weight_t / 1000000, color = dom_source)) +
  geom_line() +
  scale_color_manual(values = c("#D38F35", "#114F59", "grey")) +
  theme_bw() +
  labs(x = "", y = "Live weight\nmillion tonnes", color = "Source") +
  theme(
    legend.position = "bottom",
    legend.box.margin=margin(t = -25)
  )

@@

```{r, eval=FALSE}
# Plots moved from end of prep_data
top_processing_countries %>%
  filter(year == 2019) %>%
  ggplot(aes(x = live_weight_t, y = reorder(exporter_iso3c, ranking))) +
  geom_bar(stat = "identity") +
  scale_y_reordered() +
  theme_bw() +
  labs(x = "Re-exports (Live weight tonnes)", y = "Processing Country")

top_processing_countries_by_source %>%
  filter(year == 2019) %>%
  ggplot(aes(x = live_weight_t / 1000000, y = reorder(exporter_iso3c, ranking), fill = habitat_method)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  theme_bw() +
  labs(x = "Re-exports (Live weight million tonnes)", y = "Processing Country") +
  facet_wrap(~habitat_method, scales = "free_y")
